The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-09-16 paper/Analisis.tex
New text & plots in off-center section

>>>>

As a primer approach we study the angular dependency in the same manner as
we do in section(). In Fig. \ref{fig:OCflux} the angular for two different
off-center distribution the bold line shows an off center sphere located
at $0.5 R$ of the homogeneous sphere, while the narrow line shows sphere 
located at $0.25 R$. This is done for the model with $\tau=10^{5}$ and 
$V=50 km s^{-1}$, we find that the maximum change in flux would be up to.

\begin{figure}
\includegraphics[scale=0.3]{mu_OC.png}
\caption{Flux angular dependency for Off-center distribution, different line widths illustrate different
off-center positions.
   \label{fig:OCflux}} 
\end{figure}

The outgoing spectra for two different spheres located at $-0.25R$ and $0.25R$ respectively
is shown in Fig. \ref{fig:OCspectra}, we have shown this positions because
they are the most sensitive to rotational velocities. We found that off-center emission 
would generate asymmetric spectra, in particular depending in the location of the 
sphere the double peak would came out with different heights.

\begin{figure}
\includegraphics[scale=0.3]{OC_5t_vel100.jpg}
\caption{Spectra for two off-center spheres
   \label{fig:OCspectra}} 
\end{figure}
